Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
break 80 line char

\textcolor{red}{Say that we use PCA to derive the precision matrix + ref!.}

@@

In this section, we will first describe datasets and methods used for the
comparison. Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show
the contribution of each stages . Afterwards, we will perform a comparison
between several methods on Fig.\ref{fig:curves} and Tab.\ref{tab:tab1}. Note that two
metrics are used to evaluate the performance and a single low-pass filter is used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end of this section is
devoted to a discussion about the choice of metric and its relevance for the
challenge.\\

>>>>

@@

In this section, we will first describe datasets and methods used for the
comparison. Then, on Tab.\ref{tab:tab3}, our approach is decomposed to show
the contribution of each stages . Afterwards, we will perform a comparison
between several methods on Fig.\ref{fig:curves} and Tab.\ref{tab:tab1}. Note that two
metrics are used to evaluate the performance and a single low-pass filter is
used (Eq.\ref{eq:symetric-median}) and a threshold, i.e. $\tau = 0.11$. The end
of this section is devoted to a discussion about the choice of metric and its
relevance for the challenge.
